---
title: "Portfolio Summary"
author: "Gryffindor"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Risk Classification

The risk simulation is based on research on the benefit of repeated sampling in understanding risk conducted by the University of Mannheim. See <http://simulator.behavioral-finance.de/#!/> for further information. The portfolio is constructed according to the risk assessment conducted in the beginning of the App, where each risk class corresponds to a yearly standard deviation as a proxy for risk.


## Investment Universe

The portfolio has been constructed in accordance with the country and industry preferences specified. Geographically, your portfolio includes securities listed in the following countries: `r input$mymap_groups`. 
```{r echo=FALSE, results='asis'}
if (is.null(input$industry1)) {
        cat("In terms of industries, you did not specify any restrictions, 
            i.e. all industries are used in the portfolio construction.")
    } else {
        cat("The industries that have been chosen to exclude are: ")
        cat(input$industry1, sep = ", ")
        cat(".")
}
```


## Your Performance

```{r echo = FALSE, results = "hide", fig.align='center', out.width= "65%"}
if (input$rpref2 == 1 && input$inv_horizon <= 5) {

        portfoliofinal <<- indexpf(as.data.frame(shortbond))

        portfolioplot <- cbind(ovr$Date,portfoliofinal)
        names(portfolioplot) <- c("Date","Portfolio")
        portfolioplot$Date <- strptime(as.character(portfolioplot$Date), "%d/%m/%Y")
        portfolioplot$Date <- as.Date(format(portfolioplot$Date, "%Y-%m-%d"))
        portfolioplot <- cbind(portfolioplot, benchmark)
        
        plotfinal <- ggplot()+
          geom_line(data = portfolioplot, aes(
            Date, Portfolio, group = 1, colour = "Your Portfolio"), size = 1) +
          geom_line(data = portfolioplot, aes(
            Date, benchmark, group = 1, colour = "MSCI World Benchmark"), size =1) +
          labs(x = "Year", y = "Portfoliodevelopement",
               title = "Short Bond Portfolio") +
          scale_x_date(date_breaks = "2 years")+
          scale_colour_manual("", values = c("Your Portfolio"="blue", 
                                           "MSCI World Benchmark"="grey"))+
          theme(legend.position=c(.9,.1))
          theme_minimal()
      }

##### long bond only ###########################################################

      if ((input$rpref2 == 2 && input$inv_horizon <= 5) ||
          (input$rpref2 == 1 && input$inv_horizon > 5 &&
           input$inv_horizon <= 10)) {

        portfoliofinal <<- indexpf(as.data.frame(longbond))
        equityinvestment <<- 0

        portfolioplot <- cbind(ovr$Date,portfoliofinal)
        names(portfolioplot) <- c("Date","Portfolio")
        portfolioplot$Date <- strptime(as.character(portfolioplot$Date), "%d/%m/%Y")
        portfolioplot$Date <- as.Date(format(portfolioplot$Date, "%Y-%m-%d"))
        portfolioplot <- cbind(portfolioplot, benchmark)
        
        plotfinal <- ggplot()+
          geom_line(data = portfolioplot, aes(
            Date, Portfolio, group = 1, colour = "Your Portfolio"), size = 1) +
          geom_line(data = portfolioplot, aes(
            Date, benchmark, group = 1, colour = "MSCI World Benchmark"), size =1) +
          labs(x = "Year", y = "Portfoliodevelopement",
               title = "Long Bond Portfolio") +
          scale_x_date(date_breaks = "2 years")+
          scale_colour_manual("", values = c("Your Portfolio"="blue", 
                                             "MSCI World Benchmark"="grey")) +
          theme(legend.position=c(.9,.1))
          theme_minimal()
      }



##### minimum variance PF ######################################################

      if ((input$rpref2 == 3 && input$inv_horizon <= 5) ||
         #redundant but included so that the number of conitions = number of PFs
          (input$rpref2 == 3 && input$inv_horizon > 5 &&
           input$inv_horizon <= 10) ||
          (input$rpref2 == 2 && input$inv_horizon > 10)) {

####### split the required input df into sub-df's to make them optimizable #####
        finaldata <- datasplit(newData())
        portfoliofinal <<- minvarpf(finaldata)
        equityinvestment <<- 0

####### include the performance plot in Shiny ##################################
        portfolioplot <- cbind(ovr$Date,portfoliofinal)
        names(portfolioplot) <- c("Date","Portfolio")
        portfolioplot$Date <- strptime(as.character(portfolioplot$Date), "%d/%m/%Y")
        portfolioplot$Date <- as.Date(format(portfolioplot$Date, "%Y-%m-%d"))
        portfolioplot <- cbind(portfolioplot, benchmark)

        plotfinal <- ggplot()+
          geom_line(data = portfolioplot, aes(
            Date, Portfolio, group = 1, colour = "Your Portfolio"), size = 1) +
          geom_line(data = portfolioplot, aes(
            Date, benchmark, group = 1, colour = "MSCI World Benchmark"), size =1) +
          labs(x = "Year", y = "Portfoliodevelopement",
               title = "Minimum Variance Portfolio") +
          scale_x_date(date_breaks = "2 years")+
          scale_colour_manual("", values = c("Your Portfolio"="blue", 
                                             "MSCI World Benchmark"="grey")) +
          theme(legend.position=c(.9,.1))
        theme_minimal()

        }

###### Equity + longbond overweight bond #######################################

      if (input$rpref2 == 1 && input$inv_horizon > 10) {

        finaldata <- datasplit(newData())

        finalpf <- optimpf(finaldata)

        longbondindexed <- indexpf(as.data.frame(longbond))
        portfoliofinal <<- equityanddeptpf(finalpf, longbondindexed, 0.2)
        
        
        portfolioplot <- cbind(ovr$Date,portfoliofinal)
        names(portfolioplot) <- c("Date","Portfolio")
        portfolioplot$Date <- strptime(as.character(portfolioplot$Date), "%d/%m/%Y")
        portfolioplot <- cbind(portfolioplot, benchmark)
        
        plotfinal <- ggplot()+
          geom_line(data = portfolioplot, aes(
            Date, Portfolio, group = 1, colour = "Your Portfolio"), size = 1) +
          geom_line(data = portfolioplot, aes(
            Date, benchmark, group = 1, colour = "MSCI World Benchmark"), size =1) +
          labs(x = "Year", y = "Portfoliodevelopement",
               title = "Sharpe Ratio optimized Equity Portfolio with 80% Longterm Debt") +
          scale_x_date(date_breaks = "2 years")+
          scale_colour_manual("", values = c("Your Portfolio"="blue", 
                                             "MSCI World Benchmark"="grey")) +
          theme(legend.position=c(.9,.1))
          theme_minimal()

        equityinvestment <<- 0.2
      }

############################ risk parity #######################################
      if ((input$rpref2 == 4 && input$inv_horizon <= 5) ||
         (input$rpref2 == 5 && input$inv_horizon <= 5) ||
         (input$rpref2 == 4 && input$inv_horizon > 5 && input$inv_horizon <= 10) ||
         (input$rpref2 == 5 && input$inv_horizon > 5 && input$inv_horizon <= 10) ||
         (input$rpref2 == 3 && input$inv_horizon > 10) ||
         (input$rpref2 == 4 && input$inv_horizon > 10)) {

        finaldata <- datasplit(newData())

        finalpf <- optimpf(finaldata)

        longbonddf <- as.data.frame(longbond)
        commoditydf <- as.data.frame(commodities)

        portfoliofinal <<- riskparitypf(finalpf, longbonddf, commoditydf)
        equityinvestment <<- as.numeric(portfoliofinal[2])
        portfoliofinal <<- as.data.frame(portfoliofinal[1])

        portfolioplot <- cbind(ovr$Date, portfoliofinal)
        names(portfolioplot) <- c("Date","Portfolio")
        portfolioplot$Date <- strptime(as.character(portfolioplot$Date), "%d/%m/%Y")
        portfolioplot$Date <- as.Date(format(portfolioplot$Date, "%Y-%m-%d"))
        portfolioplot <- cbind(portfolioplot, benchmark)
        
        plotfinal <- ggplot()+
          geom_line(data = portfolioplot, aes(
            Date, Portfolio, group = 1, colour = "Your Portfolio"), size = 1) +
          geom_line(data = portfolioplot, aes(
            Date, benchmark, group = 1, colour = "MSCI World Benchmark"), size =1) +
          labs(x = "Year", y = "Portfoliodevelopement",
               title = "Risk Parity Portfolio with Sharpe Ratio optimized Equity Part") +
          scale_x_date(date_breaks = "2 years")+
          scale_colour_manual("", values = c("Your Portfolio"="blue", 
                                             "MSCI World Benchmark"="grey")) +
          theme(legend.position=c(.9,.1))
          theme_minimal()

      }

########################### equity + longbond overweight equity ################
      if ((input$rpref2 == 6 && input$inv_horizon <= 5) ||
         (input$rpref2 == 6 && input$inv_horizon > 5 && input$inv_horizon <= 10) ||
         (input$rpref2 == 5 && input$inv_horizon > 10)) {

        finaldata <- datasplit(newData())

        finalpf <- optimpf(finaldata)

        longbondindexed <- indexpf(as.data.frame(longbond))
        portfoliofinal <<- equityanddeptpf(finalpf, longbondindexed, 0.8)
        equityinvestment <<- 0.8

        portfolioplot <- cbind(ovr$Date,portfoliofinal)
        names(portfolioplot) <- c("Date","Portfolio")
        portfolioplot$Date <- strptime(as.character(portfolioplot$Date), "%d/%m/%Y")
        portfolioplot$Date <- as.Date(format(portfolioplot$Date, "%Y-%m-%d"))
        portfolioplot <- cbind(portfolioplot, benchmark)
        
        plotfinal <- ggplot()+
          geom_line(data = portfolioplot, aes(
            Date, Portfolio, group = 1, colour = "Your Portfolio"), size = 1) +
          geom_line(data = portfolioplot, aes(
            Date, benchmark, group = 1, colour = "MSCI World Benchmark"), size =1) +
          labs(x = "Year", y = "Portfoliodevelopement",
               title = "Sharpe Ratio optimized Equity Portfolio with 20% Longterm Debt") +
          scale_x_date(date_breaks = "2 years")+
          scale_colour_manual("", values = c("Your Portfolio"="blue", 
                                             "MSCI World Benchmark"="grey")) +
          theme(legend.position=c(.9,.1))
          theme_minimal()

      }

################################ Pure Equity? ##################################
      if ((input$rpref2 == 6 && input$inv_horizon > 10) ||
          (input$rpref2 == 7 && input$inv_horizon <= 5) ||
          (input$rpref2 == 7 && input$inv_horizon > 5 && input$inv_horizon <= 10) ||
          (input$rpref2 == 7 && input$inv_horizon > 10)) {

        finaldata <- datasplit(newData())

        portfoliofinal <<- optimpf(finaldata)
        equityinvestment <<- 1

        portfolioplot <- cbind(ovr$Date,portfoliofinal)
        names(portfolioplot) <- c("Date","Portfolio")
        portfolioplot$Date <- strptime(as.character(portfolioplot$Date), "%d/%m/%Y")
        portfolioplot$Date <- as.Date(format(portfolioplot$Date, "%Y-%m-%d"))
        portfolioplot <- cbind(portfolioplot,benchmark)
        
        plotfinal <- ggplot()+
          geom_line(data = portfolioplot, aes(
            Date, Portfolio, group = 1, colour = "Your Portfolio"), size = 1) +
          geom_line(data = portfolioplot, aes(
            Date, benchmark, group = 1, colour = "MSCI World Benchmark"), size = 1) +
          labs(x = "Year", y = "Portfoliodevelopement",
               title = "Sharpe Ratio optimized 100% Equity Portfolio") +
          scale_x_date(date_breaks = "2 years")+
          scale_colour_manual("", values = c("Your Portfolio"="blue", 
                                             "MSCI World Benchmark"="grey")) +
          theme(legend.position=c(.9,.1))
          theme_minimal()
      }
      plotfinal
```


```{r echo = FALSE, results='asis'}
if (input$rpref2 == 1 && input$inv_horizon <= 5) {
  cat("You have chosen a risk preference of level", input$rpref2, ", and an investment horizon of", input$inv_horizon, "years. According to these
      specifications we have identified a pure bond investment as the most
      suitable for you.")

        
      }

##### long bond only ###########################################################

      if ((input$rpref2 == 2 && input$inv_horizon <= 5) ||
          (input$rpref2 == 1 && input$inv_horizon > 5 &&
           input$inv_horizon <= 10)) {
       cat("You have chosen a risk preference of level", input$rpref2, ", and an investment horizon of", input$inv_horizon, "years. According to these
      specifications we have identified a pure bond investment as the most
      suitable for you.")


      }

##### minimum variance PF ######################################################

      if ((input$rpref2 == 3 && input$inv_horizon <= 5) ||
         #redundant but included so that the number of conitions = number of PFs
          (input$rpref2 == 3 && input$inv_horizon > 5 &&
           input$inv_horizon <= 10) ||
          (input$rpref2 == 2 && input$inv_horizon > 10)) {

####### split the required input df into sub-df's to make them optimizable #####
        cat("You have chosen a risk preference of level", input$rpref2, ", and an investment horizon of", input$inv_horizon, "years. According to these
      specifications we have identified a minimum variacne investment as the most
      suitable for you.")

        }

###### Equity + longbond overweight bond #######################################

      if (input$rpref2 == 1 && input$inv_horizon > 10) {
        cat("You have chosen a risk preference of level", input$rpref2, ", and an investment horizon of", input$inv_horizon, "years. According to these
      specifications we have identified an equity and long bond investment as the most
      suitable for you, where bond are overweighted.")

        
      }

############################ risk parity #######################################
      if ((input$rpref2 == 4 && input$inv_horizon <= 5) ||
         (input$rpref2 == 5 && input$inv_horizon <= 5) ||
         (input$rpref2 == 4 && input$inv_horizon > 5 && input$inv_horizon <= 10) ||
         (input$rpref2 == 5 && input$inv_horizon > 5 && input$inv_horizon <= 10) ||
         (input$rpref2 == 3 && input$inv_horizon > 10) ||
         (input$rpref2 == 4 && input$inv_horizon > 10)) {
        cat("You have chosen a risk preference of level", input$rpref2, ", and an investment horizon of", input$inv_horizon, "years. According to these
      specifications we have identified a risk parity investment strategy as the most
      suitable for you.")

        

      }

########################### equity + longbond overweight equity ################
      if ((input$rpref2 == 6 && input$inv_horizon <= 5) ||
         (input$rpref2 == 6 && input$inv_horizon > 5 && input$inv_horizon <= 10) ||
         (input$rpref2 == 5 && input$inv_horizon > 10)) {
          cat("You have chosen a risk preference of level", input$rpref2, ", and an investment horizon of", input$inv_horizon, "years. According to these
      specifications we have identified an equity and long bond investment as the most
      suitable for you, where equity is overweighted.")

        

      }

################################ Pure Equity? ##################################
      if ((input$rpref2 == 6 && input$inv_horizon > 10) ||
          (input$rpref2 == 7 && input$inv_horizon <= 5) ||
          (input$rpref2 == 7 && input$inv_horizon > 5 && input$inv_horizon <= 10) ||
          (input$rpref2 == 7 && input$inv_horizon > 10)) {
        cat("You have chosen a risk preference of level", input$rpref2, ", and an investment horizon of", input$inv_horizon, "years. According to these
      specifications we have identified a pure equity investment as the most
      suitable for you.")

        
      }
```

**Performance Metrics**. Historically, the portfolio that has been construceted 
for you has had an average return of `r paste0(round((averagereturn(portfoliofinal) * 100)), "%")` 
and a yearly standard derviation of `r paste0(round((yearlystd(portfoliofinal) * 100)), "%")`. 
This means that after `r input$inv_horizon` years, i.e. the investment horizon that you have
specified, you can expect a terminal wealth of `r as.character(round(((1+(averagereturn(portfoliofinal)))^input$inv_horizon)*input$initial_wealth))`.
Regarding downside risk, the portfolio has experienced a maximum drawdown of `r paste0(round((maxdrawdown(portfoliofinal) * 100)), "%")`, indicating the maximum
loss that has historically occured. Finally, the portfolio has a sharpe ratio of
`r round((averagereturn(portfoliofinal)/yearlystd(portfoliofinal)), 2)`, which shows
the magnitude of the compensation for each unit of risk taken in terms of return
in excess of the risk free rate.









